For purposes of this Agreement, the capitalized terms set forth on Exhibit A shall have the definitions that are ascribed to them below:

\begin{enumerate}[label=\Alph*.]
    \item "\textbf{Affiliate}" means, with respect to any Person, another Person that directly or indirectly, through one or more intermediaries, controls, is controlled by, or is under common control with, such first Person.

    \item "\textbf{Assets}" means the crypto-assets transacted on or in connection with an Eligible Funds Rescue in relation to the Protocol.

    \item "\textbf{Claim}" means all past, present and future disputes, claims, controversies, demands, rights, obligations, liabilities, actions and causes of action of every kind and nature (whether matured or unmatured, absolute or contingent, known or unknown, suspect or unsuspected, disclosed or undisclosed).

    \item "\textbf{Damages}" means any loss, damage, injury, decline in value, lost opportunity, Liability, claim, demand, settlement, judgment, award, fine, penalty, tax, fee (including reasonable attorneys' fees), charge, costs (including costs of investigation) or expense of any nature.

    \item "\textbf{Entity}" means any corporation (including any non-profit corporation), general partnership, limited partnership, limited liability partnership, joint venture, estate, trust, company (including any limited liability company or joint stock company), firm or other enterprise, association, organization or entity.

    \item "\textbf{Governmental Entity}" means any: (a) nation, multinational, supranational, state, commonwealth, province, territory, county, municipality, district or other jurisdiction of any nature; (b) federal, state, provincial, local, municipal, foreign or other government; (c) instrumentality, subdivision, department, ministry, board, court, administrative agency or commission or other governmental Entity, authority or instrumentality or political subdivision thereof; or (d) any quasi-governmental or private body exercising any executive, legislative, judicial, regulatory, taxing, importing or other governmental functions.

    \item "\textbf{Intellectual Property License}" means any license, sublicense, right, covenant, non-assertion, permission, immunity, consent, release or waiver under or with respect to any Intellectual Property Rights or Technology.

    \item "\textbf{Intellectual Property Rights}" means any and all rights in intellectual property and/or industrial property anywhere in the world, whether arising under statute, common law or otherwise.

    \item "\textbf{Legal Proceeding}" means any action, suit, litigation, arbitration, claim, proceeding (including any civil, criminal, administrative, investigative or appellate proceeding), hearing, inquiry, audit, examination or investigation commenced, brought, conducted or heard by or before, or otherwise involving, any court or other Governmental Entity or any arbitrator or arbitration panel.

    \item "\textbf{Legal Requirement}" means any: (a) federal, state, local, municipal, foreign, supranational or other law, statute, constitution, treaty, principle of common law, directive, resolution, ordinance, code, rule, regulation, judgment, ruling or requirement issued, enacted, adopted, promulgated, implemented or otherwise put into effect by or under the authority of any Governmental Entity; or (b) order, writ, injunction, judgment, edict, decree, ruling or award of any arbitrator or any court or other Governmental Entity.

    \item "\textbf{Liability}" means any debt, obligation, duty or liability of any nature (including any unknown, undisclosed, unmatured, unaccrued, unasserted, contingent, indirect, conditional, implied, vicarious, derivative, joint, several or secondary liability), regardless of whether such debt, obligation, duty or liability is immediately due and payable.

    \item "\textbf{Parties}" means the Protocol Community, Protocol Community Members and Whitehats participating in the Program, to whom these Terms apply.

    \item "\textbf{Person}" means any individual, Entity or Governmental Entity.

    \item "\textbf{Program}" means the process set out in this Agreement to incentivize Eligible Funds Rescues whereby a Whitehat may seek to conduct an Exploit and transfer Tokens to the Asset Recovery Address as further detailed in this Agreement.

    \item "\textbf{Representatives}" of a Person means such Person's officers, directors, employees, agents, attorneys, accountants, advisors and representatives.

    \item "\textbf{SEAL}" means the Open Security Alliance Inc., a Texas corporation.

    \item "\textbf{Technology}" means any and all: (a) technology, formulae, algorithms, procedures, processes, methods, techniques, ideas, know-how, creations, inventions, discoveries, and improvements (whether patentable or unpatentable and whether or not reduced to practice); (b) technical, engineering, manufacturing, product, marketing, servicing, business, financial, supplier, personnel and other information and materials; (c) specifications, designs, industrial designs, models, devices, prototypes, schematics and development tools; (d) software, websites, content, images, logos, graphics, text, photographs, artwork, audiovisual works, sound recordings, graphs, drawings, reports, analyses, writings, and other works of authorship and copyrightable subject matter; and (e) databases and other compilations and collections of data or information.
\end{enumerate}
