Participation in the Security Alliance Whitehat Safe Harbor Agreement (the "Program") carries a high degree of consequential risk. You should carefully consider the risks described below together with information presented in the Summary of the Program available at [\_\_\_\_\_\_\_\_\_\_] and the version of the Program Agreement maintained by the protocol which you wish to engage in advance of engaging it under the terms of the Agreement. Also consulting tax and legal advisors in advance of participation is also strongly recommended.

\subsubsection*{Terms capitalized below are defined in the template Protocol Agreement found at [\_\_\_\_\_\_\_\_\_\_].}

\subsubsection*{The Protocol Community must properly implement the Program for the Protocol you are targeting before you engage the Program}\label{exhibit:e:implementation}

You should confirm that the Protocol Community has properly implemented the Program, including by reviewing the applicable Adoption Form, before participating in the Program. If the Program is not properly implemented, it is likely that some or all of the terms of the Program Agreement will be unenforceable, which could expose you to liability from claims from certain Protocol Community Members or other Users.

\subsubsection*{You are expected to have experience with and expert-level knowledge of blockchain systems and cybersecurity as a condition of your participation}\label{exhibit:e:expertise}

Given the nature of the activities that you will perform by participating in the Program, you should be highly skilled as a cybersecurity professional and believe that you will likely be able to succeed in your attempted rescue of the Protocol. If you cannot make these commitments, you should seriously consider the potential risks before engaging in the Program, including the risk that you might inadvertently violate relevant laws or regulations by seeking to undertake an Eligible Funds Rescue.

\subsubsection*{Failing to notify the Protocol Community that you are attempting a rescue may block your ability to obtain the Reward}\label{exhibit:e:notification}

As provided for in the Program Agreement, you should notify the Protocol Community that you are engaging in the Program, proper ways to contact the Protocol Community will be provided in the Program Agreement.

\subsubsection*{Failure to successfully send all Returnable Assets to the Asset Recovery Address may prevent you from getting a Bounty}\label{exhibit:e:asset_transfer}

Certain Protocol Communities may require you to deposit all Returnable Assets to the Asset Recovery Address, and failure to do so could constitute a violation of the terms of the Agreement. Moreover, even if you put a lot of work into trying to save assets or succeed in recovering \textit{most} of them, there is no guarantee that you will receive any sort of reward or compensation for your effort and time.

\subsubsection*{Legal proceedings ongoing, pending, or threatened against you may make you ineligible for the Program}\label{exhibit:e:legal_proceedings}

If you are involved in any legal proceedings or think you may be before completing your obligations and receiving your Reward under the Program Agreement, you should not engage the Program.

\subsubsection*{You agree to follow certain procedures in case you become eligible for a Bounty and it is not delivered in a timely manner or the amount of the Bounty is disputed}\label{exhibit:e:dispute_procedures}

The Protocol Agreement details resolution steps to be taken if there is disagreement over the Bounty amount; however, you will not be able to sue any other party to the Program Agreement because of this disagreement.

\subsubsection*{You will be responsible for any tax liability incurred as a result of receiving the Bounty}\label{exhibit:e:tax_liability}

The Protocol Community will not assist you in filing or structuring the Bounty for tax treatment in a way not described in the Program Agreement. You should be familiar with your tax obligations in your local jurisdiction before engaging the Program.

\subsubsection*{This Program cannot protect you from incurring criminal, regulatory, or other liability as a result of your participation}\label{exhibit:e:liability_limits}

Although the Program may shield you from certain claims brought by the Protocol Community and its Members, no contract is able to prevent or preempt criminal, regulatory, or other liability. Moreover, legal claims may still be brought against you by third parties, who are not subject to this Agreement and its release provisions.

\subsubsection*{No partnership or endorsement is formed among you and any member of the Protocol Community}\label{exhibit:e:no_partnership}

The Protocol Community is not engaging you as a partner, agent, or contractor. No relationship beyond that arising from being a party to the Program Agreement is formed through participation in the Program.

\subsubsection*{Indemnity of Protocol Community, Members, Affiliates}\label{exhibit:e:indemnity}

In cases where members of the Protocol Community or their Affiliates incur liability to others as a result of your actions under the Program, you will indemnify (reimburse their expenses) those parties.

\subsubsection*{You agree to follow certain procedures in case there is a dispute about the Agreement}\label{exhibit:e:dispute_agreement}

In case there is a dispute about the Program Agreement, you will not be able to sue any party to the Agreement. Instead, your dispute must be arbitrated in the jurisdiction of the Singapore International Commercial Court using the rules of the Singapore International Arbitration Centre.

\subsubsection*{The Agreement may not be enforceable in all jurisdictions or against all relevant persons}\label{exhibit:e:enforceability}

The default jurisdiction of the Program is under the Singapore International Commercial Court. Although the Agreement is a legally binding contract, it cannot be guaranteed to be enforceable in all jurisdictions or under all circumstances. Some people in the Protocol Community and some third parties may still have claims against you that cannot be released through this Agreement.

\subsubsection*{You understand that if you profit in any way other than the Bounty, you may incur significant risk of liability}\label{exhibit:e:profit_risks}

Profiting in other ways from conducting this Exploit may constitute securities or commodities manipulation or fraud and has been prosecuted in that fashion in the past. Engaging in fraudulent or manipulative conduct is not covered by the release of liability under this program.
